Missing data: Current practice in football research and recommendations for improvement

### 2020-10-15 paper/paper.Rmd
first pass at establishing drake plan

```{r libraries, message = FALSE}
library(tidyverse)
library(naniar)
library(visdat)
library(patchwork)
library(fitzRoy)
library(mice)
library(truncnorm)
library(janitor)
```

@@

@@

```{r}

>>>>

```{r libraries, message = FALSE}
library(tidyverse)
library(naniar)
library(visdat)
library(patchwork)
library(fitzRoy)
library(mice)
library(truncnorm)
library(janitor)
library(drake)
```

```{r load-funs}
pivot_var <- function(data, var){
  data %>% 
    select(title,
           reviewer,
           {{ var }}) %>% 
    pivot_wider(names_from = reviewer,
                values_from = {{ var }})
}

agree_var <- function(data, var){
  statement_agree <- pivot_var(data, {{ var }}) %>% 
    select(reviewer_1, reviewer_2) %>% 
    irr::agree()

  statement_agree$value
}

```{r read-data}
gs_football <- readr::read_rds(here::here("data",
                           "gs-football.rds"))
```

```{r load-drake}
# loadd()
```

@@

```{r agree-var}
agree_var(gs_football, any_missing_data_statement)
agree_var(gs_football, any_statement_about_mcar_mnar_mar)
agree_var(gs_football, were_missing_data_explored)
agree_var(gs_football, was_imputation_used)
agree_var(gs_football, was_data_shared)

# identify table of mismatches  
gs_football %>% 
  group_by(reviewer) %>% 
  count(any_missing_data_statement)  %>% 
  pivot_wider(names_from = reviewer,
              values_from = n)
```

@@

```{r afl-stats, cache = TRUE}
